### 2016-12-26 paper/evaluation.tex
updated subjects and setup sections

We used the Github's Search API~\cite{githubsearch} to fetch Java
projects based on Maven according to the following criteria: primary
language must be Java\footnote{In case of projects in multiple
languages, the Github API considers the predominant language as the
primary language.}; project with at least 100 stars; latest update on
(or after) January 1st, 2016; contains the string \emph{mvn} in the
\emph{README} file.  The number of stars indicates the interest and
appreciation from the community to a given project.
\Comment{(https://help.github.com/articles/about-stars/)} Although our
criteria is subjective, it is an approximation to find relevant
projects to conduct our study.  Figure~\ref{fig:subject-query}
illustrates the query.

@@

\end{lstlisting}
\caption{\label{fig:subject-query} Query to the Github API for
    projects in Java with at least 100 stars, updated on January 1st,
    2016 (or later), and contains the string \emph{mvn} in the
    \emph{README} file.}
\end{figure}

As in December 12th, 2016, our search criteria returned 589 subjects.
From the 589 downloaded projects, we considered 312 projects that we
were able to compile and test. The others 277 could not be considered
because 39 were not Maven projects, 26 could not fetch all required
dependencies, 125 could not be compiled, and 87 could not execute the
tests. In addition, we first attempted to consider Gradle and Ant
projects but most of Gradle projects were related to Android apps and
libraries and adding support to Ant would require to parse the
\emph{build.xml} to identify the compilation and test commands since
the build process is based on user-defined tasks.

@@

To run our experiments, we used a \emph{Core i7-4790} (3.60 GHz) Intel
processor machine with 8 virtual CPUs (4 cores with 2 native threads
each) and 16GB of memory, running \emph{Ubuntu 14.04 LTS Trusty Tahr}
(64-bit version). Software settings include the Linux \emph{sysstat}
package to measure performance, \emph{git} to fetch subjects,
\emph{Java 8} and \emph{Maven 3} to build and test subjects, and
\emph{Python 3.4} to run our evaluation scripts. For replication, we
provide all the source artifacts publicly available at \Fix{create
gh-pages}, including supporting scripts (\eg, the script that test
subjects and generates the raw data), the full list of projects, and a
\emph{Vagrantfile} to emulate our hardware and all software
dependencies properly configured.

>>>>

We are interested to evaluate non-trivial test suites on popular
projects that are in activity. In addition, we used Maven as a
reference due to its popularity on Java projects and to automate our
evaluation. We used the Github's Search API~\cite{githubsearch} to
fetch Java projects with Maven support according to the following
criteria: (1) the primary language must be Java\footnote{In case of
projects in multiple languages, the Github API considers the
predominant language as the primary language.}; (2) the project has at
least 100 stars; (3) latest update on (or after) January 1st, 2016;
(4) the \emph{readme} file contains the string \emph{mvn}.

On Github, when a user adds a star to a project, s/he demonstrated
appreciation and bookmarked it for later
reference~\cite{github-stars}.  Although there is not a specific range
for the number of stars, our criteria is an estimation to avoid
trivial subjects. The fourth criteria is an approximation to find
projects with Maven support. The rationale is that if the string
\emph{mvn} exists in the \emph{readme} file, it may represents a Maven
call in the instructions on how to compile (or test) the project.
Figure~\ref{fig:subject-query} illustrates the query.

@@

\end{lstlisting}
\caption{\label{fig:subject-query} Query to the Github API for
    projects in Java with at least 100 stars, updated on January 1st,
    2016 (or later), and \emph{readme} file contains the string
    \emph{mvn}. Output listed in descending order of stars}
\end{figure}

As of December 12th 2016, our search criteria returned 589 subjects.
From the 589 downloaded projects, we considered 312 projects that we
were able to compile and test. The others 277 could not be considered
because 39 were not Maven projects, 26 could not fetch all required
dependencies, 125 could not be compiled, and 87 could not execute the
tests.

@@

To run our experiments, we used a \emph{Core i7-4790} (3.60 GHz) Intel
processor machine with 8 virtual CPUs (4 cores with 2 native threads
each) and 16GB of memory, running \emph{Ubuntu 14.04 LTS Trusty Tahr}
(64-bit version). Software settings include \Comment{the Linux
\emph{sysstat} package to measure performance, }\emph{git} to fetch
subjects, \emph{Java 8} and \emph{Maven 3} to build and test subjects,
and \emph{Python 3.4} to run our evaluation scripts. For replication,
all source artifacts are publicly available at \Fix{create gh-pages},
including supporting scripts (\eg, the script that test subjects and
generates the raw data), the full list of projects, and a
\emph{Vagrantfile} to emulate our hardware and all software
dependencies.
